%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Craig Hutcheon} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{1.5cm} \= \hspace{2cm} \= \kill % Spacing within the block
{\bf Address} \> 2R 114 Arklay Street,\\ % Address line 1
\> Dundee, DD37LL \\ % Address line 2
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{1.5cm} \= \hspace{2cm} \= \kill % Spacing within the block
{\bf Mobile} \> 07747 447787 \\ % Mobile phone
{\bf Email} \> \href{mailto:craighutcheon333@outlook.com}{craighutcheon333@outlook.com} \\ % Email address
{\bf LinkedIn} \> \href{https://www.linkedin.com/in/craig-hutcheon-234420163}{linkedin.com/in/craig-hutcheon-234420163} \\ % LinkedIn address
\end{tabbing}}

\vspace{-3mm}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}
Currently, a Software Engineer at N-able that is adaptable and keen learn new technologies. I can demonstrate working knowledge in many aspects of modern software development such as Agentic AI, CI/CD, Object-Oriented programming, Cloud Architecture and automation. Possessing good team working skills in varied work environments, my current goal is to grow as a software engineer, sharpening my skill set to push myself towards more senior roles.

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}
\job
{Oct 2022 -}{Present}
{N-able}
{https://www.n-able.com}
{Software Engineer}
{Through my time at N-able, I was a member of multiple teams spanning multiple projects, from N-able's Cloud management offering to its latest Agentic AI offering. This position upskilled me and given me many opportunities to grow as an engineer, working with modern tech stacks and technology. I progressed from Software Engineer I to Software Engineer II in my time at N-able, giving me the experience required to push for more senior roles.

\vspace{2mm}
\textbf{Attributes:}
\begin{itemize-noindent}
\item {Agentic AI Development – Given my time on N-able's first Agentic AI product, I was involved in developing A2A compliant Agents, to help our customers manage their devices. Through this project I was involved in developing not only the agents and our multi-agent architecture, but our agent tooling via MCP servers, and was given the opportunity to expand this knowledge with a trip to AWS re:Invent, where I learned about how the industry is progressing to an Agentic AI future.}
\item {Cloud Development – During my time at N-able, I was also involved in the CC Platform Team, who were involved in Architecting, and Developing the core components of the new product. With this, I was exposed to both AWS and Azure technologies and best practices for both.}
\item {Team Focus – As a mid-level engineer, I am expected to help the more junior members of the team grow their skills, and impart my knowledge via documentation and pair programming.}
\end{itemize-noindent}

\vspace{2mm}
\textbf{Key Skills:}
\begin{itemize-noindent}
\item {AI development (primarily in Go) with AWS Bedrock, Genkit, MCP and A2A.}
\item {AI testing principles, including red teaming, with promptfoo.}
\item {Asynchronous programming and the use of SAGA patterns via KNative.}
\item {Experience with AWS components and deployment via IaC (Terraform).}
\item {Kubernetes deployment via Kustomize.}
\item {Angular front-end development with dev extreme components and GraphQL clients.}
\item {Apollo GraphQL certifications and experience developing with Sub/Supergraph architecture.}
\item {gRPC, GraphQL and REST API development with Golang, C\# and node.}
\item {CI/CD Development via Jenkins.}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Aug 2019 -}{Oct 2022}
{NCR Corporation, XFS Integration Test Team}
{https://www.ncr.com}
{Software Engineer}
{The XFS IT Team in Dundee is a small team tasked with testing components of NCR's XFS ATM Software product and the support of hardware test with software utilities. The XFS product is shipped with every NCR ATM in the world and is responsible for the hardware drivers and APIs to control them. Being a member of this team involves working independently on different tasks and projects whilst coordinating with different development teams and stakeholders.

\vspace{2mm}
\textbf{Attributes:}
\begin{itemize-noindent}
\item {QA Process Experience – Assisted in the testing of software components to be included in the NCR XFS Software stack ensuring that critical bugs weren't missed before delivering to customers.}
\item {Independent Worker - Designed and developed an automated robotic hardware test application. This consisted of an application on the ATM alongside a Universal Robots collaborative robot. This solution helped ease the lack of manual testing during Covid lockdown periods and ensured that transaction targets could still be met.}
\item {Experience with CI/CD - Designed and implemented a process to migrate SVN projects to GitHub. This involved creating a CI/CD pipeline where none had previously existed. This has led to quality improvements of both tools and scripts.}
\end{itemize-noindent}

\vspace{2mm}
\textbf{Key Skills:}
\begin{itemize-noindent}
\item {Desktop development with C\# and WPF.}
\item {MVVM and dependency injection with Prism framework.}
\item {Unit testing experience with XUnit framework.}
\item {Dependency mocking experience with NSubstitute.}
\item {Database design and implementation with SQLite and Entity Framework Core.}
\item {Robotics programming with Universal Robots URScript.}
\item {CI/CD with GitHub Actions, SonarQube and Artifactory JFrog.}
\item {Kubernetes cluster management with Azure Kubernetes Service.}
\item {Issue tracking and management with Atlassian JIRA.}
\item {Backend web development with ASP.NET SignalR.}
\item {Win32 API Development using C++ and NCR CEN XFS APIs.}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{June 2018 -}{Aug 2018}
{Blue2 Digital}
{https://www.blue2.co.uk}
{Summer Intern}
{During my internship, I conducted R\&D in the field of headless Content Management Systems. This mainly involved migrating data from current Blue2 websites to several well-known headless CMS's to discover how difficult it may be to migrate and how doing so could help with the company's workflow.}

\vspace{2mm}
\textbf{Key Skills and Attributes:}
\begin{itemize-noindent}
\item {Experience in Web Development – I used a wide range of technologies relevant to the current market including HTML, CSS, JavaScript and hugely increased my knowledge in PHP.}
\item {Can Present Work in Front of an Audience - At the end of my placement I had to present my findings to the stakeholders and then the company.}
\end{itemize-noindent}
}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\education
{Sep 2012 -}
{Jun 2019}
{University of Dundee}
{https://www.dundee.ac.uk/}
{2:1 BSc (Hons) Applied Computing HCI\\
Previously studied BEng (Hons) in Civil Engineering at the University of Dundee. Changed to BSc Applied Computing HCI in 2016.}

%------------------------------------------------

\education
{Sep 2005 -}
{Jun 2012}
{Mintlaw Academy}
{}
{6 Highers: Maths, English, Technological Studies, Graphic Communication, Product Design, Physics}

\end{document}